Sensor Clusterization in D-optimal Design in Infinite Dimensional Bayesian Linear Inverse Problems

### 2024-08-25 revision/rev3.tex
answered refs

\begin{quote}
  In the proof of Theorem \ref{thm:char} we utilize Lemma
\ref{lemma:free} to construct D-optimal designs. We implement this
construction with the goal of testing numerically how prevalent are
clustered designs. To this end, we would like to generate random prior
eigenvalues $\lambda_j$, fix $m$ and $k$, find a D-optimal
$\opt^*\opt$ and then utilize the construction of
Theorem~\ref{thm:char} and Lemma~\ref{lemma:free} to find $\opt$.

To simplify things, we directly sample rank $\opt^*\opt$. We iterate
over the number of measurements $m \in \{4,\dots, 24\}$, and for every
$m$ we then iterate over $k:=\rank \obs^*\obs \in \{2,\dots,
m-1\}$. For each pair $m,k$ we repeat the following steps $N=5000$
times:
\begin{enumerate}
\item Generate random diagonal $D\in \mathbb{R}^{k\times k}$ with
  entries $\log (d_i) \sim \mathcal{N}(50,15)$ and normalize so that
  $\ttr D = m$. 
\item Conjugate $D$ by a random orthogonal matrix to form a positive
  semi-definite $M := UDU^t \in \mathbb{R}^{k\times k}$. This $M$
  represents $\opt^*\opt$.
\item Apply the construction of Lemma \ref{lemma:free} to calculate
  $A$ such that $AA^t = M$, where $A$ has unit norm columns. I.e.~find
  the optimal design $\opt$.
\item Since $A$ corresponds to $\opt$, its columns correspond to
  measurement vectors. We call $A$ "clustered" if $A$ has two or more
  identical columns (up to some numerical precision threshold).
\end{enumerate}
We then calculate the fraction of clustered designs of the simulations
we ran, for each pair $m,k$. Clusterization occurred at high rates
($>99.9\%$) whenever $m-k > 1$; see Fig.~\ref{fig:sim_AAt}. Hence, in
these simulations, clusterization is a generic property. However, when
$m-k = 1$, clusterization does not occur. We do not why this is so and
further investigation into this phenomenon is out of scope for the
current study.

Full results are located in the \texttt{simulations.csv} file within
the accompanying \href{https://github.com/yairdaon/OED}{repository}.
Code implementing the experiments described above is located in module
\texttt{zeros.py} of said repository. Runtime should be less than 30
minutes on any reasonably modern laptop (it took 12 minutes on the
author's laptop).
\end{quote}

@@

\AR I added a discussion on this subject. I do not argue against the
use of clustered designs imply that clustered designs, but I believe
that when they arise it should be a warning signal to a practitioner
regarding the validity of their physical model and Bayesian
assumptions:

\begin{quote}
  DO THIS FML!!!!!!
\end{quote}

@@

\RC Experiment with the 1D heat equation: the experiment showcases
some interesting phenomena, but also raises many questions. For
instance: I would expect the dimensionality of the working domain
(here the unit interval $[0, 1]$) to play a role, since larger
dimension allow for higher freedom in placing the design points.

\AR Say something??? FML

\RC Further, a dimensionality effect should also arise directly from
Theorem 1 via the prior covariance eigenvalues: in the experiment the
prior covariance operator is set to be equal to the inverse Laplace
operator $(-\Delta)^{-1}$. In d-dimensional domains, its eigenvalues
$\lambda_j$ are known to follow Weyl’s asymptotics, growing as
$j^{2/d}$, which should then impact the index after which the
eigenvalues are ‘thresholded’ by the procedure.

\AR These are two great points. Indeed, the growth of eigenvalues of
the Laplacian is different in higher dimensions. This is why in higher
dimensions we would have to take as prior \(u_0 \sim
\mathcal{N}(\param_0, (-\Delta)^{-\gamma})\), for some \(\gamma >
d/2\) in order to maintain regularity of prior realizations. I decided
not to include a discussion on the choice of priors in higher spatial
dimensions because (1) it would require too much exposition and make
me digress from the main points I wanted to convey and (2) I view
implementing experiments in higher dimensions as out of the scope of
the current study.

@@

\begin{quote}
  In order to verify the results of Section
  \ref{section:non_vanishing}, we run simulations of the inverse
  problem of the 1D heat equation with nonvanishing model error
  \(\modcov = \prcov^2 \). Indeed, including model correlation pushes
  measurements apart, see Fig.~\ref{fig:corr_errors}. Code generating
  Fig.~\ref{fig:corr_errors} is located in module
  \texttt{clusterization.py} in the accompanying
  \href{https://github.com/yairdaon/OED}{repository}.
\end{quote}
\begin{figure}
  \centering
  \includegraphics[height=0.5\textwidth]{figs/dst_modelError4.png}
  \caption{Model correlation mitigates clusterization. We add a
    model correlation term to the error terms in the 1D heat
    equation inverse problem. Lo and behold, measurements are not
    close anymore and are pushed away thanks to the model error
    term.}
    \label{fig:corr_errors}
\end{figure}

@@

\AR I removed the statement of Theorem 1 from the introduction.

\RC Denoting the optimal design in Theorem 1 by simply $\obs$ is
somewhat confusing, cf. the equation in the second item. Perhaps a
separate notation such as $\bar{\obs}$ would help readability.

@@

\begin{quote}
  It is worth noting that by the nonnegativity of the KL divergence,
  $\tar$ cannot decrease upon adding measurements. However, we can
  construct examples where the posterior does not change upon taking a
  new measurement e.g.~if the prior variance vanishes on some
  eigenvector and a measurement is taken on said eigenvector. We do
  not expect a measurement to generate no information gain whatsoever
  in any realistic scenario, and ignore such pathologies.
\end{quote}

@@

\begin{quote}
  Clusterization should not be confused with replication. Replication
  requires that the experimentalist executes multiple trials under
  circumstances that are \emph{nominally identical} \cite[Section
    1.2.4]{morris2011}. Replication is commonly viewed as a beneficial
  and even necessary aspect of optimal experimental design
  \cite{fisher1949design, morris2011, schafer2001replication}. Similarly
  to a design implementing replication, a clustered design reduces the
  signal-to-noise ratio of the repeated measurements
  \cite{telford2007brief}. The difference is that a clustered design
  takes repeated measurements at the expense of other quantities not
  measured at all.
\end{quote}

@@

\AR the Mat\'ern-like prior actually arises by using a Laplacian-like
operator as a prior \cite{rue2011}. So a study of this example (with
and without correlated errors) is already included in the paper. I am
afraid implementing another inverse problem is out of scope for the
present paper since I was not able to install common packages for
inverse problems \cite{attia2023pyoed, VillaPetraGhattas16,
  VillaPetraGhattas18, VillaPetraGhattas21} on my machine.

@@

\AR Indeed, point evaluations $\delta_x$ are not in any function space
I consider in the paper since my analysis is limited to Hilbert
spaces. Point evaluations can be approximated well in
e.g.~$L^2(\Omega)$ so in my opinion this is not a deal breaker. The
only caveat is that upon approximating point evaluations e.g.~by
$R(x;t) = t\mathbb{1}_{-t/2, t/2}(x)$ we will need to change the norm
constraints to the something different (i.e.~$\|R(\cdot;t\|$) but that
does not change the analysis. I barely mentioned this issue in the
paper since I think it is confusing and adds little context. See,
however, a footnote I added which is reproduced below:

\begin{quote}
  The alert reader will likely ask how do we reconcile point
  measurements $\delta_x$ as suggested by the formulation of the 1D
  heat equation with working in Hilbert spaces. We don't. We follow
  standard practice in the literature and restrict our analysis to
  Hilbert spaces. We can satisfy ourselves with the fact that point
  evaluations could be approximated in a standard Hilbert space like
  $L^2(\Omega)$.
\end{quote}

@@

\begin{quote}
  Building on Theorem \ref{thm:char}, we can now give a compelling
  explanation to the measurement clusterization we observed for the
  inverse problem of the heat equation (Fig.~\ref{fig:eigenvectors}).

  Consider $\fwd$ and $\prcov$ from \emph{the inverse problem of the
  heat equation}. As before, we denote the eigenvalues of
  $\fwd\prcov\fwd^*$ by $\lambda_j$. We input these eigenvalues into
  our \emph{generic} model, and find a D-optimal design $\opt$ for our
  generic model using Theorem \ref{thm:char}. In our generic model,
  the measurements we take are best utilized in reducing uncertainty
  for the first $k$ eigenvectors. So, a D-optimal design arising from
  our \emph{generic model} completely avoids measuring eigenvectors
  $k+1$ and above.

  Of course, in a real life problem --- such as the inverse problem of
  the 1D heat equation --- it is likely impossible to find measurement
  locations for which all eigenvectors $k+1$ and above are
  zero. However, if the eigenvalues of $\fwd\prcov\fwd^*$ decay
  quickly (recall the square-exponential decay for eigenvalues of the
  1D heat equation in eq.\eqref{eq:decay}), a D-optimal design will
  try to balance measuring a small number (i.e.~$k$) of the leading
  eigenvectors.

  The abovementioned balance is explored in
  Fig.~\ref{fig:eigenvectors}. We allow $m=4$ measurements in $\Omega
  = [0,1]$ and observe that D-optimal measurement locations are
  clustered at $x_1 = 0.31$ and $x_2 = 0.69$. Upon close inspection of
  the scaled eigenvectors of $\fwd \prcov \fwd^*$, we first observe
  that eigenvectors $3$ and above have negligible prior
  amplitude. Since we only have $m=4$ measurements at our disposal, we
  interpret these results, following Theorem \ref{thm:char}, as
  implying we should only care about measuring the first and second
  eigenvectors. Then, we note the D-optimal $x_1,x_2$ present a
  compromise between the amplitude of the first and second
  eigenvectors. For example, a measurement at $x=0.5$ would have
  ignored the second eigenvector altogether, since the second
  eigenvector is zero at $x=0.5$.

  Now we can understand measurement clusterization for the inverse
  problem of the heat equation. A D-optimal design attempts to measure
  the first $k$ eigenvectors of $\fwd \prcov \fwd^*$. But there may be
  (spatial) limitations on where these $k$ eigenvectors have large
  amplitude. For the inverse problem of the heat equation there are
  two spatial locations that present a good compromise between the
  amplitudes of the first and second eigenvectors, namely $x_1$ and
  $x_2$ --- see Fig.~\ref{fig:eigenvectors}. We have $m=4$
  measurements at our disposal but only two spatial locations that are
  a good compromise between the first and second scaled
  eigenvectors. Thus, clusterization arises as a consequence of the
  pigeonhole principle.

\end{quote}

\begin{figure}\label{fig:eigenvectors}
  \centering
  \includegraphics[width=\textwidth]{figs/eigenvectors_dst_scaled.png}
  \caption{D-optimal measurement locations ($m=4$ measurements) and
    weighted eigenvectors for finding the initial condition of the 1D
    heat equation. Measurement locations and weighted eigenvectors are
    plotted over the computational domain $\Omega = [0, 1]$
    (x-axis). Measurement clusterization occurs approximately at
    $0.31$ and $0.69$. These two locations are a compromise between
    the magnitudes of the first and second eigenvectors, which are the
    eigenvectors that a D-optimal design aims to measure. Allocating
    $m=4$ measurements into two locations results in clusterization,
    according to the pigeonhole principle.}
  \label{fig:why}
\end{figure}

>>>>

\begin{quote} %% Simulate
  In the proof of Theorem \ref{thm:char} we utilize Lemma
  \ref{lemma:free} to construct D-optimal designs. We implement this
  construction with the goal of testing numerically how prevalent are
  clustered designs. To this end, we would like to generate random
  prior eigenvalues $\lambda_j$, fix $m$ and $k$, find a D-optimal
  $\opt^*\opt$ and then utilize the construction of
  Theorem~\ref{thm:char} and Lemma~\ref{lemma:free} to find $\opt$.
  \newline
  To simplify things, we directly sample rank $\opt^*\opt$. We iterate
  over the number of measurements $m \in \{4,\dots, 24\}$, and for
  every $m$ we then iterate over $k:=\rank \obs^*\obs \in \{2,\dots,
  m-1\}$. For each pair $m,k$ we repeat the following steps $N=5000$
  times:
  \begin{enumerate}
  \item Generate random diagonal $D\in \mathbb{R}^{k\times k}$ with
    entries $\log (d_i) \sim \mathcal{N}(50,15)$ and normalize so that
    $\ttr D = m$.
  \item Conjugate $D$ by a random orthogonal matrix to form a positive
    semi-definite $M := UDU^t \in \mathbb{R}^{k\times k}$. This $M$
    represents $\opt^*\opt$.
  \item Apply the construction of Lemma \ref{lemma:free} to calculate
    $A$ such that $AA^t = M$, where $A$ has unit norm
    columns. I.e.~find the optimal design $\opt$.
  \item Since $A$ corresponds to $\opt$, its columns correspond to
    measurement vectors. We call $A$ "clustered" if $A$ has two or
    more identical columns (up to some numerical precision threshold).
  \end{enumerate}
  We then calculate the fraction of clustered designs of the
  simulations we ran, for each pair $m,k$. Clusterization occurred at
  high rates ($>99.9\%$) whenever $m-k > 1$; see
  Fig.~\ref{fig:sim_AAt}. Hence, in these simulations, clusterization
  is a generic property. However, when $m-k = 1$, clusterization does
  not occur. We do not why this is so and further investigation into
  this phenomenon is out of scope for the current study.
  \newline
  Full results are located in the \texttt{simulations.csv} file within
  the accompanying \href{https://github.com/yairdaon/OED}{repository}.
  Code implementing the experiments described above is located in
  module \texttt{zeros.py} of said repository. Runtime should be less
  than 30 minutes on any reasonably modern laptop (it took 12 minutes
  on the author's laptop).
\end{quote}

@@

\AR I added a discussion on this subject. In the manuscript this
discussion is broken in two since the second part relies on Theorem
\ref{thm:char}. Thus, the first part is in the Introduction and the
second part follows the statement and proof of the abovementioned
theorem. I believe the level of discussion is adequate and view a
deeper analysis of convergence rates as out of scope for the current
study.
\begin{quote}%%Convergence
  Given that D-optimal designs suffer from clusterization, it is
  natural to ask whether D-optimal designs should be pursued at
  all. Other authors have established convergence results for decaying
  measurement error \cite{knapik2011}, space-filling measurements
  \cite{teckentrup2020} and randomly sampled designs
  \cite{nickl2023}. Unfortunately, D-optimal designs --- clustered
  designs in particular --- do not fall into any of these categories.
  \newline
  Luckily, we can expect convergence from D-optimal designs (including
  clustered designs). Convergence holds in the following sense: the
  posterior uncertainty ellipsoid in $\hilo$ will contract to zero
  along every eigenfunction of $\fwd \prcov \fwd^*$. See Section
  \ref{subsub:convergence} for a proof based on Theorem \ref{thm:char}
  --- the main theorem of this manuscript.
  \newline
  Below we fulfill our promise from Section \ref{subsub:implications}
  and prove that the posterior uncertainty ellipsoid in $\hilo$ will
  contract to zero along every eigenfunction of $\fwd \prcov
  \fwd^*$. In our proof we ignore potential problems with conducting
  inference on function spaces which are not unique to D-optimal
  designs (see e.g.~\ref{owhadi2015} for more details).
  \newline
  First, let $\opt_m$ a D-optimal design utilizing $m$
  measurements. Then, an immediate consequence of Theorem
  \ref{thm:char} is that $\rank \opt_m^*\opt_m = k \to \infty$ as the
  number of measurements $m \to \infty$. Moreover, part (5) of Theorem
  \ref{thm:char} ensures that the eigenvalues of the posterior
  covariance equal
  \begin{equation*}
    \theta^{(k)}_i = \left ( \frac{\sum_{j=1}^k \lambda_j^{-1} +
      \sigma^{-2}m}{k} \right )^{-1}, \text{ for $i\leq k$},
  \end{equation*}
  where we explicitly express the dependence of $k$ in the
  superscript. Now note that $\theta^{(k)}_i \leq \lambda_i$ for
  $i\leq k$. Specifically, for fixed $k$, we get $\theta^{(k)}_i \leq
  \lambda_k$ for all $i\leq k$. Since $\lim_{k\to \infty} \lambda_k=
  0$, we conclude that for all $i$, $\lim_{k\to\infty} \theta^{(k)}_i
  = 0$. Since $m\to \infty$ implies $k\to \infty$ we have
  $\lim_{m\to\infty} \theta^{(k)}_i = 0$ for all $i$. Therefore,
  posterior uncertainty decays to zero for all eigenvectors.
\end{quote}

@@

\RC Experiment with the 1D heat equation: the experiment showcases
some interesting phenomena, but also raises many questions. For
instance: I would expect the dimensionality of the working domain
(here the unit interval $[0, 1]$) to play a role, since larger
dimension allow for higher freedom in placing the design points.
Further, a dimensionality effect should also arise directly from
Theorem 1\footnote{Now denoted Theorem \ref{thm:char}.} via the prior
covariance eigenvalues: in the experiment the prior covariance
operator is set to be equal to the inverse Laplace operator
$(-\Delta)^{-1}$. In d-dimensional domains, its eigenvalues
$\lambda_j$ are known to follow Weyl’s asymptotics, growing as
$j^{2/d}$, which should then impact the index after which the
eigenvalues are ‘thresholded’ by the procedure.

\AR These are two great points. Indeed, the growth of eigenvalues of
the Laplacian is different in higher dimensions. This is why in higher
dimensions we would have to take as prior \(u_0 \sim
\mathcal{N}(\param_0, (-\Delta)^{-\gamma})\), for some \(\gamma >
d/2\) in order to maintain regularity of prior realizations. I decided
not to include a discussion on the choice of priors in higher spatial
dimensions because (1) it would require too much exposition and make
me digress from the main points I wanted to convey and (2) due to
technical difficulties in installing packages for inverse problems
\cite{attia2023pyoed, VillaPetraGhattas16} I had to implement the
inverse problem of the 1D heat equation from scratch, so I decided to
leave out experiments in higher dimensions.

@@

\begin{quote}
  In order to verify the results of Section
  \ref{section:non_vanishing}, we run simulations of the inverse
  problem of the 1D heat equation with nonvanishing model error
  \(\modcov = \prcov^2 \). Indeed, including model correlation pushes
  measurements apart, see Fig.~\ref{fig:corr_errors}. Code generating
  Fig.~\ref{fig:corr_errors} is located in module
  \texttt{clusterization.py} in the accompanying
  \href{https://github.com/yairdaon/OED}{repository}.
\end{quote}
\begin{figure}
  \centering
  \includegraphics[height=0.5\textwidth]{../latex/figs/dst_modelError4.png}
  \caption{Model correlation mitigates clusterization. We add a
    model correlation term to the error terms in the 1D heat
    equation inverse problem. Lo and behold, measurements are not
    close anymore and are pushed away thanks to the model error
    term.}
    \label{fig:corr_errors}
\end{figure}

@@

\AR I removed the statement of Theorem 1 from the introduction. It is
Theorem \ref{thm:char} now.

\RC Denoting the optimal design in Theorem 1 by simply $\obs$ is
somewhat confusing, cf.~the equation in the second item. Perhaps a
separate notation such as $\bar{\obs}$ would help readability.

@@

\begin{quote}%% Pathologies
It is worth noting that by the nonnegativity of the KL divergence,
$\tar$ cannot decrease upon adding measurements. However, we can
construct examples where the posterior does not change upon taking a
new measurement e.g.~if the prior variance vanishes on some
eigenvector and a measurement is taken on said eigenvector. We do not
expect a measurement to generate no information gain whatsoever in any
realistic scenario, and ignore such pathologies.
\end{quote}

@@

\begin{quote} %% Replication
Clusterization should not be confused with replication. Replication
requires that the experimentalist executes multiple trials under
circumstances that are \emph{nominally identical} \cite[Section
  1.2.4]{morris2011}. Replication is commonly viewed as a beneficial
and even necessary aspect of optimal experimental design
\cite{fisher1949design, morris2011, schafer2001replication}. Similarly
to a design implementing replication, a clustered design reduces the
signal-to-noise ratio of the repeated measurements
\cite{telford2007brief}. The difference is that a clustered design
takes repeated measurements at the expense of other quantities not
measured at all.
\end{quote}

@@

\AR the Mat\'ern-like prior actually arises by using a Laplacian-like
operator as a prior \cite{rue2011}. So a study of this example (with
and without correlated errors) is already included in the paper. I am
afraid implementing another inverse problem is out of scope for the
present paper since I was not able to install common packages for
inverse problems \cite{attia2023pyoed, VillaPetraGhattas16} on my
machine.

@@

\AR Indeed, point evaluations $\delta_x$ are not in any function space
I consider in the paper since my analysis is limited to Hilbert
spaces. Point evaluations can be approximated well in
e.g.~$L^2(\Omega)$ so in my opinion this is not a deal breaker. For
example, we can replace point evaluations by $R(x;t) =
t\mathbb{1}_{-1/2t, 1/2t}(x)$, where $\mathbb{1}$ is an indicator
function. We will then need to change the norm constraints on
measurement vectors from unit to $\|R(\cdot;t\|^2 = \int R^2(x;t)dx =
t$ norm but that does not change the analysis as long as $t$ is
fixed. I barely mentioned this issue in the paper since I think it is
confusing and adds little context. See a footnote I added:

\begin{quote} %% Footnote
  The alert reader will likely ask how do we reconcile point
  measurements $\delta_x$ as suggested by the formulation of the 1D
  heat equation with working in Hilbert spaces. We don't. We follow
  standard practice in the literature and restrict our analysis to
  Hilbert spaces. We can satisfy ourselves with the fact that point
  evaluations could be approximated in a standard Hilbert space like
  $L^2(\Omega)$.
\end{quote}

@@

\begin{quote}
  Building on Theorem \ref{thm:char}, we can now give a compelling
  explanation to the measurement clusterization we observed for the
  inverse problem of the heat equation, see Section
  \ref{subsub:clusterization1} below. We also suggest a generic
  explanation for clusterization, see Section
  \ref{subsub:clusterization2}.
  \newline
  Consider $\fwd$ and $\prcov$ from \emph{the inverse problem of the
  heat equation}. As before, we denote the eigenvalues of
  $\fwd\prcov\fwd^*$ by $\lambda_j$. We input these eigenvalues into
  our \emph{generic} model, and find a D-optimal design $\opt$ for our
  generic model using Theorem \ref{thm:char}. In our generic model,
  the measurements we take are best utilized in reducing uncertainty
  for the first $k$ eigenvectors. So, a D-optimal design arising from
  our \emph{generic model} completely avoids measuring eigenvectors
  $k+1$ and above.
  \newline
  Of course, in a real life problem --- such as the inverse problem of
  the 1D heat equation --- it is likely impossible to find measurement
  locations for which all eigenvectors $k+1$ and above are
  zero. However, if the eigenvalues of $\fwd\prcov\fwd^*$ decay
  quickly (recall the square-exponential decay for eigenvalues of the
  1D heat equation in eq.\eqref{eq:decay}), a D-optimal design will
  try to balance measuring a small number (i.e.~$k$) of the leading
  eigenvectors.
  \newline
  The abovementioned balance is explored in
  Fig.~\ref{fig:eigenvectors}. We allow $m=4$ measurements in $\Omega
  = [0,1]$ and observe that D-optimal measurement locations are
  clustered at $x_1 = 0.31$ and $x_2 = 0.69$. Upon close inspection of
  the scaled eigenvectors of $\fwd \prcov \fwd^*$, we first observe
  that eigenvectors $3$ and above have negligible prior
  amplitude. Since we only have $m=4$ measurements at our disposal, we
  interpret these results, following Theorem \ref{thm:char}, as
  implying we should only care about measuring the first and second
  eigenvectors. Then, we note the D-optimal $x_1,x_2$ present a
  compromise between the amplitude of the first and second
  eigenvectors. For example, a measurement at $x=0.5$ would have
  ignored the second eigenvector altogether, since the second
  eigenvector is zero at $x=0.5$.
  \newline
  Now we can understand measurement clusterization for the inverse
  problem of the heat equation. A D-optimal design attempts to measure
  the first $k$ eigenvectors of $\fwd \prcov \fwd^*$. But there may be
  (spatial) limitations on where these $k$ eigenvectors have large
  amplitude. For the inverse problem of the heat equation there are
  two spatial locations that present a good compromise between the
  amplitudes of the first and second eigenvectors, namely $x_1$ and
  $x_2$ --- see Fig.~\ref{fig:eigenvectors}. We have $m=4$
  measurements at our disposal but only two spatial locations that are
  a good compromise between the first and second scaled
  eigenvectors. Thus, clusterization arises as a consequence of the
  pigeonhole principle.
\end{quote}

\begin{figure}\label{fig:eigenvectors}
  \centering
  \includegraphics[width=\textwidth]{../latex/figs/eigenvectors_dst_scaled.png}
  \caption{D-optimal measurement locations ($m=4$ measurements) and
    weighted eigenvectors for finding the initial condition of the 1D
    heat equation. Measurement locations and weighted eigenvectors are
    plotted over the computational domain $\Omega = [0, 1]$
    (x-axis). Measurement clusterization occurs approximately at
    $0.31$ and $0.69$. These two locations are a compromise between
    the magnitudes of the first and second eigenvectors, which are the
    eigenvectors that a D-optimal design aims to measure. Allocating
    $m=4$ measurements into two locations results in clusterization,
    according to the pigeonhole principle.}
  \label{fig:why}
\end{figure}
